---
title: "Lab 01 - Hello R!"
date: "2022-09-13"
author: "Meherab Hossain"
output: 
  html_document: 
    self_contained: no
    fig_width: 10
    fig_height: 6
    highlight: espresso
    theme: cosmo
  tufte::tufte_html:
    tufte_variant: "envisioned"
    highlight: pygments
    css: lab.css
    link-citations: yes
    self_contained: FALSE
---

```{r include=FALSE}
library(tidyverse)
library(datasauRus)
options(
  htmltools.dir.version = FALSE, # for blogdown
  show.signif.stars = FALSE     # for regression output
  )
```



# Data
&nbsp;

#### 1. Based on the help file, how many rows and how many columns does the `datasaurus_dozen` file have? What are the variables included in the data frame?
&nbsp;


**The dataset contains $1846$ rows and $3$ columns. The variables are x-values and y-values and data set.**  
&nbsp;





# Data visualization and summary
&nbsp;




#### 2. Plot `y` vs. `x` for the `dino` dataset. Then, calculate the correlation coefficient between `x` and `y` for this dataset.

&nbsp;



**We pipe and filter the appropriate dataset and assign it to a variable.**
```{r}
dino_data = datasaurus_dozen %>%
  filter(dataset == "dino")
```

**We plot the data as a scatter point plot **
```{r fig.fullwidth=TRUE, fig.height=6, fig.width=6}
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


**Using the following chunk of code we calculate the correlation coefficient, $r_{d}$, to be $-0.0645$ **
```
dino_data %>%
  summarize(r = cor(x, y))
```
&nbsp;






#### 3. Plot `y` vs. `x` for the `star` dataset. You can (and should) reuse code we introduced above, just replace the dataset name with the desired dataset. Then, calculate the correlation coefficient between `x` and `y` for this dataset. How does this value compare to the `r` of `dino`?
&nbsp;


 
  
   
    
     
      
**We answer this similarly to the question above by simply changing datasets.**
```{r}
star_data = datasaurus_dozen %>%
  filter(dataset == "star")
```
```{r fig.fullwidth=TRUE}
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
&nbsp;
 
  
   
   
**we calculate the correlation coefficient , $r_{s}$, to be $-0.0645$. This is similar to $r_{d}$ in the sense that data does not correlate very well since they are both close to $0$. The negative symbol indicates that they increase/decrease in opposite directions. **

&nbsp;




#### 4. Plot `y` vs. `x` for the `circle` dataset. You can (and should) reuse code we introduced above, just replace the dataset name with the desired dataset. Then, calculate the correlation coefficient between `x` and `y` for this dataset. How does this value compare to the `r` of `dino`?
&nbsp;

**We apply the same methods as in the previous exercises.**

```{r}
circle_data = datasaurus_dozen %>%
  filter(dataset == "circle")
```
```{r fig.fullwidth=TRUE}
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
&nbsp;

```
dino_data %>%
  summarize(r = cor(x, y))
```
&nbsp;

**We get the following correlation coefficient, $r_{c}$ to be $-0.0683$. This is similar to $r_{s}$ and $r_{d}$ since the data does not correlate very well in the 3 datasets.**

#### 5. Finally, let's plot all datasets at once. In order to do this we will make use of facetting.

```{r all-viz, eval=FALSE, fig.fullwidth=TRUE}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

And we can use the `group_by` function to generate all the summary correlation coefficients.

```{r all-r, eval=FALSE}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

You're done with the data analysis exercises, but we'd like you to do two more things:



**I purposely removed the print command to display the whole table**


**I changed the global figure sizes and customized the dino figure to be slightly smaller. I also changed the theme.**
