---
title: "Lab 01 - Hello R!"
date: "2022-09-13"
author: "Meherab Hossain"
output: 
  html_document: 
    self_contained: no
  tufte::tufte_html:
    tufte_variant: "envisioned"
    highlight: pygments
    css: lab.css
    link-citations: yes
    self_contained: FALSE
---

```{r include=FALSE}
library(tidyverse)
library(datasauRus)
options(
  htmltools.dir.version = FALSE, # for blogdown
  show.signif.stars = FALSE     # for regression output
  )
```



# Data
&nbsp;

#### 1. Based on the help file, how many rows and how many columns does the `datasaurus_dozen` file have? What are the variables included in the data frame?
&nbsp;


**The dataset contains $1846$ rows and $3$ columns. The variables are x-values and y-values and data set.**  
&nbsp;





# Data visualization and summary
&nbsp;




#### 2. Plot `y` vs. `x` for the `dino` dataset. Then, calculate the correlation coefficient between `x` and `y` for this dataset.

&nbsp;



**We pipe and filter the appropriate dataset and assign it to a variable.**
```{r}
dino_data = datasaurus_dozen %>%
  filter(dataset == "dino")
```

**We plot the data as a scatter point plot **
```{r fig.fullwidth=TRUE}
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


**Using the following chunk of code we calculate the correlation coefficient, $r_{d}$, to be $-0.0645$ **
```
dino_data %>%
  summarize(r = cor(x, y))
```
&nbsp;






#### 3. Plot `y` vs. `x` for the `star` dataset. You can (and should) reuse code we introduced above, just replace the dataset name with the desired dataset. Then, calculate the correlation coefficient between `x` and `y` for this dataset. How does this value compare to the `r` of `dino`?
&nbsp;


 
  
   
    
     
      
**We answer this similarly to the question above by simply changing datasets.**
```{r}
star_data = datasaurus_dozen %>%
  filter(dataset == "star")
```
```{r fig.fullwidth=TRUE}
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
&nbsp;
 
  
   
   
**we calculate the correlation coefficient , $r_{s}$, to be $-0.0645$. This is similar to $r_{d}$ in the sense that data does not correlate very well since they are both close to $0$. The negative symbol indicates that they increase/decrease in opposite directions. **

&nbsp;




#### 4. Plot `y` vs. `x` for the `circle` dataset. You can (and should) reuse code we introduced above, just replace the dataset name with the desired dataset. Then, calculate the correlation coefficient between `x` and `y` for this dataset. How does this value compare to the `r` of `dino`?
&nbsp;

**We apply the same methods as in the previous exercises.**

```{r}
circle_data = datasaurus_dozen %>%
  filter(dataset == "circle")
```
```{r fig.fullwidth=TRUE}
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
&nbsp;

```
dino_data %>%
  summarize(r = cor(x, y))
```
&nbsp;

**We get the following correlation coefficient, $r_{c}$ to be $-0.0683$. This is similar to $r_{s}$ and $r_{d}$ since the data does not correlate very well in the 3 datasets.**

#### 5. Finally, let's plot all datasets at once. In order to do this we will make use of facetting.

```{r all-viz, eval=FALSE, fig.fullwidth=TRUE}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

And we can use the `group_by` function to generate all the summary correlation coefficients.

```{r all-r, eval=FALSE}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

You're done with the data analysis exercises, but we'd like you to do two more things:



- **Resize your figures:** 

Click on the gear icon in on top of the R Markdown document, and select "Output Options..." in the dropdown menu. In the pop up dialogue box go to the Figures tab and change the height and width of the figures, and hit OK when done. Then, knit your document and see how you like the new sizes. Change and knit again and again until you're happy with the figure sizes. Note that these values get saved in the YAML.



You can also use different figure sizes for different figures. To do so click on the gear icon within the chunk where you want to make a change. Turn on "Use custom figure size" and enter the size for this figure. Changing the figure sizes added new options to these chunks: `fig.width` and `fig.height`. You can change them by defining different values directly in your R Markdown document as well with code like this:

```
knitr::opts_chunk(fig.width=3, fig.height=3)
```



- **Change the look of your report:** 

Once again click on the gear icon in on top of the R Markdown document, and select "Output Options..." in the dropdown menu. In the General tab of the pop up dialogue box try out different Syntax highlighting and theme options. Hit OK and knit your document to see how it looks. Play around with these until you're happy with the look.


*Yay, you're done! Commit all remaining changes, use the commit message "Done with Lab 1!", and push. Before you wrap up the assignment, make sure all documents are updated on your GitHub repo.*

## Rubric (15 points possible)

10 points if code and descriptions are complete for all questions.
5 points for >= five commits with informative messages made to the repo.

